[Re] Spike Timing Dependent Plasticity Finds the Start of Repeating Patterns in Continuous Spike Trains

### 2018-06-27 article/Hathway-Goodman-2018.tex
changes in response to review2

\documentclass[10pt,a4paper,onecolumn]{article}
% \usepackage[utf8]{inputenc}
\usepackage{marginnote}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{authblk,etoolbox}
\usepackage{titlesec}
\usepackage{calc}
\usepackage{hyperref}
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor=
{
      Pamela Hathway,
      Dan F. M. Goodman,,
  },
            pdftitle=
{
[Re] Spike Timing Dependent Plasticity Finds the Start of Repeating Patterns
in Continuous Spike Trains
},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=blue,
            pdfborder={0 0 0}}
\urlstyle{same}
\usepackage{tcolorbox}
\usepackage{ragged2e}
\usepackage{fontspec}
%\defaultfontfeatures{Path = /usr/local/texlive/2018/texmf-dist/fonts/opentype/public/fontawesome/}
\usepackage{fontawesome}
\usepackage{caption}
\usepackage{listings}
\lstnewenvironment{code}{\lstset{language=Haskell,basicstyle=\small\ttfamily}}{}

@@

The original study models the potential of the output neuron with the
Gerstner's Spike Response model (SRM) \autocite{Gerstner2002}, which
uses kernels to calculate the effect of incoming spikes on the
postsynaptic voltage. Brian on the other hand uses differential
equations to model the system parameters and evaluates those equations
for each time step. We converted the kernels of the posystnaptic
potential and the spike afterpotential into the following differential
equations:

@@

The values for the parameters can be found in Tbl.~\ref{tbl:param}.
Eq.~\ref{eq:1} describes the postsynaptic membrane potential, which is
influenced by presynaptic excitatory postsynaptic potentials (EPSPs,
first term) and a negative afterpotential after a spike (second term).
In the event of a presynaptic spike, \(x\) is increased by 1
(\(x\leftarrow x+1\)), which initiates the voltage increase in the
postsynaptic neuron. When the postsynaptic voltage reaches the
threshold, a spike occurs: the voltage \(u\) is set to twice the
threshold (\(u\leftarrow 2T\)), all EPSPs are flushed (all \(x\) set to
0, \(x\leftarrow 0\)) and the negative afterpotential is set into motion
(\(a\) is set to 1, \(a\leftarrow 1\)). Presynaptic spikes had the same
effect on the postsynaptic neuron potential as in the original
publication as shown in Fig.~\ref{fig:pot}.

@@

\begin{figure}
\centering
\includegraphics{figures/fig4_convergence.pdf}
\caption{Weights at converged state. This figure shows a raster plot of
the input spikes at the end of the simulation (converged state) with the
color of the dots indicating the synaptic weight. The final weights in
the converged state look very similar in the the original study
(\textbf{A)}) and the replication implementation (\textbf{B)}). Weights
from neurons not involved in the pattern are close to 0 (black, neurons
1000-1999), whereas weights from some neurons involved in the pattern
(neurons 0-999) are close to 1 (white, maximum value). The weights of
neurons that spike at the beginning of the pattern are nearly all close
to 1 and their added postsynaptic potentials cause a spike at the
beginning of the pattern (blue rectangle).}\label{fig:conv}
\end{figure}

@@

If the learning rule is modified so that the change in synaptic weight
reflects that on average half the input neurons spike before the output
neuron and the other half afterwards (by adding the mean of LTP and LTD
traces), the pattern is found earlier, at around 17 s or 850 spikes (for
a time step of \(10^{-4}s\)) which is close to the performance for
smaller time steps (\(10^{-6}s\)) and the original paper (both 14 s or
700 spikes). This modified learning rule was only used to determine the
time until finding (Fig.~\ref{fig:find}) because it differs from the
implementation used in the majority of modelling papers.

@@

\begin{figure}
\centering
\includegraphics{figures/fig8_kernel_vs_imm.pdf}
\caption{Choice of EPSP. For the same presynaptic spikes, the
postsynaptic voltage behaves similarly, but the postsynaptic spike time
is slightly different (green and black dots).}\label{fig:epsps}
\end{figure}

>>>>

\documentclass[10pt,a4paper,onecolumn]{article}
% \usepackage[utf8]{inputenc}
\usepackage{marginnote}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{authblk,etoolbox}
\usepackage{titlesec}
\usepackage{calc}
\usepackage{hyperref}
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor=
{
      Pamela Hathway,
      Dan F. M. Goodman,,
  },
            pdftitle=
{
[Re] Spike Timing Dependent Plasticity Finds the Start of Repeating Patterns
in Continuous Spike Trains
},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=blue,
            pdfborder={0 0 0}}
\urlstyle{same}
\usepackage{tcolorbox}
\usepackage{ragged2e}
\usepackage{fontspec}
\usepackage{fontawesome}
\usepackage{caption}
\usepackage{listings}
\lstnewenvironment{code}{\lstset{language=Haskell,basicstyle=\small\ttfamily}}{}

@@

The original study models the potential of the output neuron with the
Gerstner's Spike Response model (SRM) \autocite{Gerstner2002}, which
uses kernels to calculate the effect of incoming spikes on the
postsynaptic voltage. Brian on the other hand uses differential
equations to model the system parameters and evaluates those equations
for each time step. The SRM kernels can be modelled using alpha
functions \autocite{Brette2007}, so we converted the kernels of the
postsynaptic potential and the spike afterpotential into the following
differential equations:

@@

The values for the parameters can be found in Tbl.~\ref{tbl:param}. We
chose the exact method for integrating the differential equations
(called `linear' in Brian). Eq.~\ref{eq:1} describes the postsynaptic
membrane potential, which is influenced by presynaptic excitatory
postsynaptic potentials (EPSPs, first term) and a negative
afterpotential after a spike (second term). In the event of a
presynaptic spike at neuron \(i\), \(x\) is increased by the respecitve
synaptic weight \(w_{i}\) (\(x\leftarrow x+w_{i}\)), which initiates the
voltage increase in the postsynaptic neuron. When the postsynaptic
voltage reaches the threshold, a spike occurs: the voltage \(u\) is set
to twice the threshold (\(u\leftarrow 2T\)), all EPSPs are flushed (all
\(x\) set to 0, \(x\leftarrow 0\)) and the negative afterpotential is
set into motion (\(a\) is set to 1, \(a\leftarrow 1\)). Presynaptic
spikes had the same effect on the postsynaptic neuron potential as in
the original publication as shown in Fig.~\ref{fig:pot}.

@@

\begin{figure}
\centering
\includegraphics{figures/fig4_convergence.pdf}
\caption{Weights at converged state. This figure shows a raster plot of
the input spikes at the end of the simulation (converged state) with the
color of the dots indicating the synaptic weight (see colorbar). The
final weights in the converged state look very similar in the the
original study (\textbf{A)}) and the replication implementation
(\textbf{B)}). Weights from neurons not involved in the pattern are
close to 0 (black, neurons 1000-1999), whereas weights from some neurons
involved in the pattern (neurons 0-999) are close to 1 (white, maximum
value). The weights of neurons that spike at the beginning of the
pattern are nearly all close to 1 and their added postsynaptic
potentials cause a spike at the beginning of the pattern (blue
rectangle).}\label{fig:conv}
\end{figure}

@@

If the learning rule is modified so that the change in synaptic weight
reflects that on average half the input neurons spike before the output
neuron and the other half afterwards (by adding the mean of LTP and LTD
traces), the pattern is found earlier, at around 17 s or 850 spikes (for
a time step of \(10^{-4}s\)) which is close to the performance for
smaller time steps (\(10^{-6}s\)) and the original paper (both 14 s or
700 spikes). This modified learning rule was only used to determine the
time until finding (Fig.~\ref{fig:find}).

@@

\begin{figure}
\centering
\includegraphics{figures/fig8_kernel_vs_imm.pdf}
\caption{Choice of EPSP. For the same presynaptic spikes, the
postsynaptic voltage behaves similarly, but the postsynaptic spike time
is slightly different
(/home/ph416/Documents/ReScience-submission/article/figures/fig8\_kernel\_vs\_imm.pdf).}\label{fig:epsps}
\end{figure}
